Combining checkpointing and data compression\\ for high frequency seismic imaging

### 2018-10-02 paper/paper.tex
Change the order of x, y, z
fix minor detail

Various strategies are routinely employed to reduce this memory requirement, for example 
Domain decomposition (TODO cite) where the domain of the simulation is distributed over
multiple nodes so as to fit within the memory available on each node. This introduces the overhead
of network communication and might not efficiently use the computational resources on each node.
Another common strategy, which is specific to the domain of FWI, is where only the boundaries of
the domain are stored at each timestep and the rest of the wavefield is reconstructed from the
boundaries when required (TODO CITE). Another commonly used strategy that is applied across
a much wider domain of problems is checkpointing. In this strategy, a subset of the data from the
forward pass is stored (and the rest discarded). The discarded data is recomputed when required
by rerunning the forward pass. Starting from Revolve (TODO cite), which was a provably optimal
scheduling algorithm to implement this strategy, various studies have used and extended this
technique to various scenarios (TODO cite other checkpointing papers).

>>>>

Various strategies are routinely employed to reduce this memory requirement, for example 
Domain decomposition (TODO cite) where the domain of the simulation is distributed over
multiple nodes so as to fit within the memory available on each node. This introduces the overhead
of network communication and might not efficiently use the computational resources on each node.
Another common strategy, which is specific to the domain of FWI, is where only the boundaries of
the domain are stored at each timestep and the rest of the wavefield is reconstructed from the
boundaries when required (TODO CITE). Another commonly used strategy that is applied across
a much wider domain of problems is checkpointing. In this strategy, a subset of the data from the
forward pass is stored (and the rest discarded). The discarded data is recomputed when required
by rerunning the forward pass. Starting from Revolve (TODO cite), which is a provably optimal
scheduling algorithm to implement this strategy, various studies have used and extended this
technique to various scenarios (TODO cite other checkpointing papers).
